Collocated Snapshot Backup with VM-Centric Deduplication in the Cloud

### 2013-09-23 snapshot_system/fast14_evaluation.tex
revise
Updated to adjusted model

 Table~\ref{tab:vm-availability} shows the availability of VM snapshots when 
there are up to 25 machine nodes failed in a 100-node cluster and  a 1000-node cluster. 
We show three snapshot  availability curves as the number of machines failed increases.
%Two VC curves use $V_c=1250$ and $V_c=2500$ representing the average number of VMs that share a PDS file system block. 
Curve ``VC(WC)" represents a worst-case  situation that each PDS file system block is shared by all VMs.
%$V_c=2500$ represents  the absolute worst case for 2500 VMs. 
%The VO curve has  $V_o=6.3$ which is the average number of VMs that share a file system block in our smaller dataset.
%To get this number, we perform perfect deduplication over 105 VMs, append unique chunks to a DFS file and
%count the number of dependencies from a file system block to VM.
%In the scenario of having 2500 VMs, this number can only increase, thus this number represents the best
%case for VO approach. 
%Our results show that the VC approach even with $V_c=2500$ has a higher availability than VO.
%For example, with 10 machines failed, VO with 98.5\% availability would lose snapshots of 37 VMs 
%while VC with 99.9\% loses snapshots of 2.5 VMs.
%The key reason is that  $N_1 +N_2 < N_o$, caused by the fact that the VM-centric approach localizes deduplication
%and packs  data blocks for one VM as much as possible.  The extra replication
%for PDS blocks also significantly increases the snapshot availability even when
%a PDS file block is shared by every VM.
%=======
%Figure~\ref{tab:vm-availability} shows the availability of VM snapshots
%as storage nodes fail. 
%We assume a random distirbution of 64MB filesystem
%blocks (FSBs). where FSBs are not randomly distributed availability might
%be improved by limiting the number of storage nodes a particualr VM depends
%on but we take the conservative approach. We compare VO, the expected case for
%VC ($V_c=p*V/2$), and the worst case for VC ($V_c=p*V/2$). We set $V_o=6.3$
%based on measured values in our dataset.
To obtain VM sharing of file blocs, we perform perfect deduplication over 105 VMs, 
append unique chunks to a DFS file and
count the number of dependencies from a file system block to VM.
%In the case of having 2500 or even 25000 VMs, this number can only increase, thus this number represents the best
%case for VO approach. 
Our results show that even the worst case for VC has a higher availability than VO.
%Our VM-centric approach shows significant improvements
%in VM availability.
For example, with 5/100 machines failed, VO with 93.3\% availability would lose data in 169 VMs 
while VC with 99.9\% loses data for 2 VMs.
The key reason is that for most data in VC, only a single
VM can be affected by the loss of a single FSB.
% because our VM-centric approach
%localizes deduplication.

@@

                    \addplot table[x=NodesFailed,y=VCWC1]{figures/node_failures_100.txt};
                    \addlegendentry{VC (worst-case)}

@@

\end{figure}
}
\begin{table}
    \footnotesize
    \tabcolsep=0.11cm
    \begin{tabular}{|l|l|l|l|l|l|l|}
        \hline
        \multirow{3}{*}{Failures}   & \multicolumn{6}{c|}{Snapshot Availability} \\
                                    %\cline{2-7}
                                    & \multicolumn{3}{c|}{$p=100$} & \multicolumn{3}{c|}{$p=1000$} \\
                                    %\cline{2-7}
                                    & VO & VC & VC(WC) & VO & VC & VC(WC) \\
        \hline
        3 & 99.304 & 99.891 & 99.891 & 99.999 & 99.999 & 99.999\\
        5 & 93.256 & 98.919 & 98.919 & 99.993 & 99.999 & 99.999\\
        10 & 43.251 & 87.707 & 87.638 & 99.919 & 99.987 & 99.987\\
        20 & 0.034 & 24.953 & 21.571 & 99.228 & 99.879 & 99.879\\
        \hline
    \end{tabular}
    \caption{Availability of VM snapshots for VO and VC.}
    \label{tab:vm-availability}
\end{table}

@@

\begin{table}
    \begin{tabular}{|c|c|c|c|c|c|}
    \hline
    Tasks & CPU & Mem &Read &  Write  & Time  \\ \hline
    & & (MB)          &(MB/s) &  (MB/s) & (hrs) \\ \hline
%    1     & 19\% & 118.1 & 50MB/s 8.37 & 1.314\\ \hline
    1     & 19\% & 118 & 50 & 8.4 & 1.31\\ \hline
%    2     & 35\% & 131.8 & 9.0 & 1.226\\ \hline
    2     & 35\% & 132 &50  & 9.0 & 1.23\\ \hline
    %4     & 63\% & 154.1 & 9.3 & 1.179\\ \hline
    4     & 63\% & 154&50   & 9.3 & 1.18\\ \hline
%    6     & 77\% & 171.9 & 9.46 & 1.162\\ \hline
%    8     & 82\% & 90.5 & 89.2 & \\ \hline
%    10                      & 85\% & 97.2   & 90.4 \\ \hline
%    12                      & 91\% & 95.6    & 91.5 \\ \hline
    \end{tabular}
\caption{Resource usage of concurrent backup tasks at each machine}
\label{tab:resource_usage}
\end{table}

>>>>

 Table~\ref{tab:vm-availability} shows the availability of VM snapshots when 
there are up to 25 machine nodes failed in a 100-node cluster and  a 1000-node cluster. 
We show three snapshot  availability curves as the number of machines failed increases.
%Two VC curves use $V_c=1250$ and $V_c=2500$ representing the average number of VMs that share a PDS file system block. 
Curve ``VC(WC)" represents a worst-case  situation that each PDS file system block is shared by all VMs.
%$V_c=2500$ represents  the absolute worst case for 2500 VMs. 
%The VO curve has  $V_o=6.3$ which is the average number of VMs that share a file system block in our smaller dataset.
%To get this number, we perform perfect deduplication over 105 VMs, append unique chunks to a DFS file and
%count the number of dependencies from a file system block to VM.
%In the scenario of having 2500 VMs, this number can only increase, thus this number represents the best
%case for VO approach. 
%Our results show that the VC approach even with $V_c=2500$ has a higher availability than VO.
%For example, with 10 machines failed, VO with 98.5\% availability would lose snapshots of 37 VMs 
%while VC with 99.9\% loses snapshots of 2.5 VMs.
%The key reason is that  $N_1 +N_2 < N_o$, caused by the fact that the VM-centric approach localizes deduplication
%and packs  data blocks for one VM as much as possible.  The extra replication
%for PDS blocks also significantly increases the snapshot availability even when
%a PDS file block is shared by every VM.
%=======
%Figure~\ref{tab:vm-availability} shows the availability of VM snapshots
%as storage nodes fail. 
%We assume a random distirbution of 64MB filesystem
%blocks (FSBs). where FSBs are not randomly distributed availability might
%be improved by limiting the number of storage nodes a particualr VM depends
%on but we take the conservative approach. We compare VO, the expected case for
%VC ($V_c=p*V/2$), and the worst case for VC ($V_c=p*V/2$). We set $V_o=6.3$
%based on measured values in our dataset.
To obtain VM sharing of file blocs, we perform perfect deduplication over 105 VMs, 
append unique chunks to a DFS file and
count the number of dependencies from a file system block to VM.
%In the case of having 2500 or even 25000 VMs, this number can only increase, thus this number represents the best
%case for VO approach. 
Our results show that even the worst case for VC has a higher availability than VO.
%Our VM-centric approach shows significant improvements
%in VM availability.
For example, with 5/100 machines failed, VO with 93.256\% availability would lose data in 169 VMs 
while VC with 97.763\% loses data for 56 VMs.
The key reason is that for most data in VC, only a single
VM can be affected by the loss of a single FSB.
% because our VM-centric approach
%localizes deduplication.

@@

                    %\addplot table[x=NodesFailed,y=VCOpt1]{figures/node_failures_100.txt};
                    %\addlegendentry{VC (CDS ordering)}

@@

\end{figure}
}
\begin{table}
    \footnotesize
    \tabcolsep=0.11cm
    \begin{tabular}{|l|l|l|l|l|l|l|}
        \hline
        \multirow{3}{*}{Failures}   & \multicolumn{6}{c|}{Snapshot Availability} \\
                                    %\cline{2-7}
                                    & \multicolumn{3}{c|}{$p=100$} & \multicolumn{3}{c|}{$p=1000$} \\
                                    %\cline{2-7}
                                    & VO & VC & VC(Opt) & VO & VC & VC(Opt) \\
        \hline
        3 & 99.304 & 99.774 & 99.774 & 99.999 & 99.999 & 99.999 \\
        5 & 93.256 & 97.763  & 97.763 & 99.993 & 99.998 & 99.998 \\
        10 & 43.252 & 76.094 & 76.214 & 99.919 & 99.974 & 99.974 \\
        20 & 0.034 & 5.614 & 7.507 & 99.228 & 99.749 & 99.749 \\
        \hline
    \end{tabular}
    \caption{Availability of VM snapshots for VO and VC.}
    \label{tab:vm-availability}
\end{table}

@@

\begin{table}
    \begin{tabular}{|c|c|c|c|c|c|}
    \hline
    Tasks & CPU & Mem &Read &  Write  & Time  \\ 
    & & (MB)          &(MB/s) &  (MB/s) & (hrs) \\ \hline
%    1     & 19\% & 118.1 & 50MB/s 8.37 & 1.314\\ \hline
    1     & 19\% & 118 & 50 & 8.4 & 1.31\\ \hline
%    2     & 35\% & 131.8 & 9.0 & 1.226\\ \hline
    2     & 35\% & 132 &50  & 9.0 & 1.23\\ \hline
    %4     & 63\% & 154.1 & 9.3 & 1.179\\ \hline
    4     & 63\% & 154&50   & 9.3 & 1.18\\ \hline
%    6     & 77\% & 171.9 & 9.46 & 1.162\\ \hline
%    8     & 82\% & 90.5 & 89.2 & \\ \hline
%    10                      & 85\% & 97.2   & 90.4 \\ \hline
%    12                      & 91\% & 95.6    & 91.5 \\ \hline
    \end{tabular}
\caption{Resource usage of concurrent backup tasks at each machine}
\label{tab:resource_usage}
\end{table}
